\subsection{Samuel's Weekly Blog Posts - Fall Term}
\subsubsection{Week 4}
Our group met with our client for the second time this week, discussing the information for the requirements document. We also met to finish up the problem statement. We have a good idea of what our project is, and plan on drawing some early mock-ups for the UI, as that is the next step to give our client something to look at.
\subsubsection{Week 5}
Our team met to discuss the tech review assignment. We were able to come up with enough technologies to analysis. No problems have come up yet. We are waiting until we have the requirements draft finished to meet with our client again.
\subsubsection{Week 6}
This week we finished the requirements document draft, as well as the tech review draft. We didn't run into any problems. The next goals are to finish the tech review final and start the design document.
\subsubsection{Week 7}
Tech reviews were completed and we had another meeting with the client concerning the requirements document. We didn't experience any problems this week. We plan on having some of the design document complete before the next meeting in two weeks.
\subsubsection{Week 8}
No real progress or problems. We are starting the design document this weekend.
\subsubsection{Week 9}
We met with our client, and presented some mock-ups of our UI layout. No problems presented themselves. We plan on finishing the design document over the weekend.
\subsection{Samuel's Weekly Blog Posts - Winter Term}
\subsubsection{Week 1}
We met with our client and showed a basic prototype of the project. We may change the software we are using, as we found a possible problem with the current one: Defold. We plan on meeting up to work with each other on Tuesday.
\subsubsection{Week 2}
Had a team meeting to designate tasks. We changed our mind on which of our techs to use, so we can accomplish stuff faster. We will meet Saturday to work on our poster.
\subsubsection{Week 3}
We presented a prototype to one of our client/experts for feedback. We ran into issues with using our chart library. We plan on improving our prototype into our first finished case by next Friday.
\subsubsection{Week 4}
We just worked on the project this week, with the goal of completing one scenario this week. We haven't run into any problems. We plan on making one more scenario next week and meet with our client.
\subsubsection{Week 6}
We finished our Alpha version and meet with our client this week. We feel confident we can complete the project on time. We only have to fix some bugs and formatting.
\subsubsection{Week 7}
Not much progress since the last client meeting. Will be working over the weekend.
\subsubsection{Week 8}
We worked on minor things and sent our alpha to one of the clients to get some feedback. We plan on fixing anything they find is problematic.
\subsubsection{Week 9}
We met with the client and discussed the final things we need to work on to complete the project. We plan on working on some of these things over the next week.
\subsubsection{Week 10}
Not a lot of progress this week. We will be working on the final video and report over the weekend.
\subsection{Samuel's Weekly Blog Posts - Spring Term}
\subsubsection{Week 1}
We are meeting with the client on Friday, and finishing up our list of issues. We plan on working on documentation next week.
\subsubsection{Week 2}
We sent an email to client for some verification. We are planning on meeting with our client Monday.
\subsubsection{Week 3}
We submitted document changes this week and we plan on meeting our client on Monday.
\subsubsection{Week 4}
We met with our client and turned in our poster. We will be having a multi-group meeting before expo, with the other groups that work with our client.
\subsubsection{Week 5}
We met with our client, and sent off our poster. Now we are just getting ready for expo.
\subsubsection{Week 6}
We met with our client and got info on the expo in class. We are ready for expo, and will work on some tweaks and documentation the following week.