\subsection{Reflection - Samuel Wilson}
\begin{enumerate}
\item \textbf{What technical information did you learn?}
During this project, I learned about the technical process of creating physics simulations, such as the math behind real world physics, and how physics engines work. I also worked exclusively with Javascript to implement our project, which allowed me to better understand the capabilities of web-based applications.
\item \textbf{What non-technical information did you learn?}
I learned more about the process of creating something for a client. It’s important to be able to describe what is happening during the projects creation, to the client, in clear language. This allows them to make decisions easier, instead of being unsure of what the problem really is.
\item \textbf{What have you learned about project work?}
Setting daily goals is important to stay productive. If given the chance to put a tasks off until tomorrow, I will. This goes together with team goals, where assigning low-level tasks becomes important, to keep people productive.
\item \textbf{What have you learned about project management?}
When starting off on a project, it is important to create some form of design documentation to use as a reference while working on the project. During the project, timelines and task lists budget the time needed to complete everything that is outlined in the design document.
\item \textbf{What have you learned about working in teams?}
Working in teams requires a constant stream of communication to be effective. Micro-goals have to be set and assigned to ensure that projects get done in a timely manner. Expectations are part of the communication, which also works to keep people on time.
\item \textbf{If you could do it all over, what would you do differently?}
One of the main problems we ran into was imperfections in the physics engine we selected. While our client was ultimately satisfied with our end product, it is clear that if we had found the limitations of the engine beforehand, we would have changed our development plan. Specifically, we would have designed a custom engine to handle the physics of pendulums, despite it taking a longer time.
\end{enumerate}